---
title: "Exercise 2.2 Data"
format: 
  html:
    self-contained: true
    embed-resources: true
editor: visual
---

## Attach packages

Run the chunk directly below to attach the `tidyverse` and `palmerpenguins` packages.

```{r}
#| label: chunk1
library(tidyverse)
library(palmerpenguins)
```

palmerpenguins gives us access to the `penguins` data frame. In the chunk below, run `data(penguins)` to make the data frame object appear in your Environment pane listing. Then examine the data frame to answer these questions, using the RStudio graphical tools and/or writing code:

-   How many rows (observations) does `penguins` have? (Hint: `?nrow`)
-   How many variables (columns) does `penguins` have, and what are their names? (Hint: `?ncol`, `?names`)

```{r}
#| label: chunk2

# your code here

```

*Check answer: (run chunk and compare code to yours)*

```{r}
#| label: chunk2-soln
writeLines(readr::read_file("src/scripts/soln-2.2-c2.R"))
```

## Manipulate a data frame

How many Gentoo penguins are there in the dataset? How many Adelie? (Hint: `dplyr::filter()`)

```{r}
#| label: chunk3
```

*Check answer:*

```{r}
#| label: chunk3-soln
writeLines(readr::read_file("src/scripts/soln-2.2-c3.R"))
```

How many female penguins were observed on Dream island?

```{r}
#| label: chunk4
```

*Check answer:*

```{r}
#| label: chunk4-soln
writeLines(readr::read_file("src/scripts/soln-2.2-c4.R"))
```

Sort the penguin observations by body weight descending. How much did the heaviest penguin weigh? What species and sex were they?

```{r}
#| label: chunk5
```

*Check answer:*

```{r}
#| label: chunk5-soln
writeLines(readr::read_file("src/scripts/soln-2.2-c5.R"))
```
