---
title: "Exercise 3.1 Distributions, scatter plots, and bar charts"
format: 
  html:
    self-contained: true
    embed-resources: true
editor: visual
---

## 1. Attach packages

Attach the `tidyverse` package below using the `library()` function.

```{r}
#| label: chunk1

# your code here

```

*Check your solution:*

```{r}
#| label: chunk1-soln
writeLines(readr::read_file("src/scripts/soln-3.1-c1.R"))
```

## 2. Load and inspect the `midwest` data set

`midwest` is a data set included with ggplot2.

1.  Run `data(midwest)` in the chunk below to load it into your Environment pane.
2.  Then use `names()` and `summary()` on `midwest` to see what are the variable (column) names, and a statistical summary on each column. How many columns are there? What is the mean `poptotal`?

```{r}
#| label: chunk2


```

*Check your solution:*

```{r}
#| label: chunk2-soln
writeLines(readr::read_file("src/scripts/soln-3.1-c2.R"))
```

## 3. Histograms

Suppose we are interested in the `area` variable of `midwest`. What is the frequency distribution of observed values? Is this a normal or skewed variable?

We can plot a histogram of any vector in base R using the `hist()` function. In chunk2, use `hist()` to make a histogram of `midwest$area`.

```{r}
#| label: chunk3


```

*Check answer:*

```{r}
#| label: chunk3-soln
writeLines(readr::read_file("src/scripts/soln-3.1-c3.R"))
```

Now let's use ggplot2 for a histogram of the same information. The base plot is already started for you in chunk3; add a `geom_histogram()` layer with an aesthetic mapping `aes()` for area.

```{r}
#| label: chunk4

ggplot(midwest)

```

*Check answer:*

```{r}
#| label: chunk4-soln 
writeLines(readr::read_file("src/scripts/soln-3.1-c4.R"))
```

Modify your last plot (copy-paste the code down) and set a bin width of 0.01.

```{r}
#| label: chunk5


```

*Check answer:*

```{r}
#| label: chunk5-soln 
writeLines(readr::read_file("src/scripts/soln-3.1-c5.R"))
```

## 4. Scatter plots

The base R function `plot()` can plot two continuous vectors as a scatter. Let's see if there is a relationship between `midwest$percprof` (percent of people employed in professions, rather than other kinds of work) and `midwest$percchildbelowpovert`. For example, perhaps we expect lower child poverty in area where there is a higher level of professional employment. Try `plot()` with these vectors.

```{r}
#| label: chunk6


```

*Check answer:*

```{r}
#| label: chunk6-soln 
writeLines(readr::read_file("src/scripts/soln-3.1-c6.R"))
```

Now let's use ggplot2 for a histogram of the same information. In chunk6, use a `geom_point()` layer with aesthetic mappings for `percprof` and `percchildbelowpovert`.

```{r}
#| label: chunk7


```

*Check answer:*

```{r}
#| label: chunk7-soln 
writeLines(readr::read_file("src/scripts/soln-3.1-c7.R"))
```

## 5. Bar charts

Make a bar chart (`geom_bar()`) showing how many observations were made for each state. Which states are we dealing with here, and how many rows for each state?

```{r}
#| label: chunk8


```

*Check answer:*

```{r}
#| label: chunk8-soln
writeLines(readr::read_file("src/scripts/soln-3.1-c8.R"))
```
