---
title: "Exercise 3.1 Distributions, scatter plots, and bar charts"
format: 
  html:
    self-contained: true
    embed-resources: true
editor: visual
---

## Attach packages

Let's attach the `tidyverse` package, but first, add a line of code to also attach `palmerpenguins`.

```{r}
#| label: chunk1
library(tidyverse)
```

## Histograms

Suppose we are interested in the `bill_depth_mm` variable of `penguins`.

We can plot a histogram of any vector in base R using the `hist()` function. In chunk2, use `hist()` to make a histogram of `penguins$bill_depth_mm`.

```{r}
#| label: chunk2

```

*Check answer:*

```{r}
#| label: chunk2-soln
writeLines(readr::read_file("src/scripts/soln-3.1-c2.R"))
```

Now let's use ggplot2 for a histogram of the same information. The base plot is already started for you in chunk3; add a `geom_histogram()` layer with an aesthetic mapping `aes()` for body mass.

```{r}
#| label: chunk3
ggplot(penguins)
```

*Check answer:*

```{r} 
#| label: chunk3-soln 
writeLines(readr::read_file("src/scripts/soln-3.1-c3.R"))
```

Modify your last plot (copy-paste the code down) and set a bin width of 0.25.

```{r}
#| label: chunk4

```

*Check answer:*

```{r} 
#| label: chunk4-soln 
writeLines(readr::read_file("src/scripts/soln-3.1-c4.R"))
```

## Scatter plots

The base R function `plot()` can plot two continuous vectors as a scatter. Try it to compare `penguins$bill_length_mm` and `penguins$bill_depth_mm`.

```{r}
#| label: chunk5

```

*Check answer:*

```{r} 
#| label: chunk5-soln 
writeLines(readr::read_file("src/scripts/soln-3.1-c5.R"))
```

Now let's use ggplot2 for a histogram of the same information. In chunk6, use a `geom_point()` layer with aesthetic mappings for `bill_depth_mm` and `bill_length_mm`.

```{r}
#| label: chunk6

```

*Check answer:*

```{r} 
#| label: chunk6-soln 
writeLines(readr::read_file("src/scripts/soln-3.1-c6.R"))
```

## Bar charts

Make a bar chart (`geom_bar()`) showing how many observations were made for each island.

```{r}
#| label: chunk7
```

*Check answer:*

```{r}
#| label: chunk7-soln
writeLines(readr::read_file("src/scripts/soln-3.1-c7.R"))
```

