---
title: "Exercise 3.2 Box plots, heat maps"
format: 
  html:
    self-contained: true
    embed-resources: true
editor: visual
---

## 1. Attach tidyverse and load `midwest`

Attach the `tidyverse` package below using the `library()` function. Then use `data()` to load the included `midwest` data set in your environment.

```{r}
#| label: chunk1

# your code here

```

*Check your solution:*

```{r}
#| label: chunk1-soln
writeLines(readr::read_file("src/scripts/soln-3.2-c1.R"))
```

## 2. Boxplots

How does the distribution of `area` vary across states? Use `geom_boxplot()` below with aesthetic mappings for `state` and `area`.

```{r}
#| label: chunk2


```

*Check answer:*

```{r}
#| label: chunk2-soln
writeLines(readr::read_file("src/scripts/soln-3.2-c2.R"))
```

## 3. 2-way category heatmaps

Let's turn our categorical variables into factors instead of character vectors. The conversion for `state` is already written below. Add equivalent commands for converting `county`, `inmetro`, and `category`. Notice that we are assigning the `mutate()` call back to the dataframe each time, overwriting the old variable with a new one.

```{r}
#| label: chunk3

midwest <- midwest %>% mutate(state = as_factor(state))


```

*Check answer:*

```{r}
#| label: chunk3-soln 
writeLines(readr::read_file("src/scripts/soln-3.1-c3.R"))
```

Following the slides, use `janitor::tabyl()` to make a 2-way table, then visualize it using `geom_tile()`.

```{r}
#| label: chunk4




```
